A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-09 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
Fixup a few reference issues with #113

An important new development in the analysis domain has been the
emergence of new analysis tools coming from industry and open-source
projects (e.g. Jupyter notebooks~\cite{http://jupyter.org/}, the scikit-learn package~\cite{scikit-learn}), and this presents new opportunities for improving the HEP
analysis software ecosystem. The HEP community is very interested in
using these software tools, together with established components, in an
interchangeable way. The main challenge will be to enable new
open-source tools to be plugged in dynamically to the existing ecosystem
and to provide mechanisms that allow the existing and new components to
interact and exchange data efficiently. To improve our ability to
analyse much larger datasets, R\&D will be needed to investigate file
formats, compression algorithms, and new ways of storing and accessing
data for analysis and to adapt workflows to run on future computing
infrastructures.

@@

Reproducibility of scientific results goes in hand with the need to preserve both the data and the software.
Section~\ref{data-and-software-preservation}} develops this latter topic where the FAIR principles of data management are embraced.

>>>>

An important new development in the analysis domain has been the
emergence of new analysis tools coming from industry and open-source
projects (e.g. Jupyter notebooks~\cite{Jupyter}, the scikit-learn package~\cite{scikit-learn}), and this presents new opportunities for improving the HEP
analysis software ecosystem. The HEP community is very interested in
using these software tools, together with established components, in an
interchangeable way. The main challenge will be to enable new
open-source tools to be plugged in dynamically to the existing ecosystem
and to provide mechanisms that allow the existing and new components to
interact and exchange data efficiently. To improve our ability to
analyse much larger datasets, R\&D will be needed to investigate file
formats, compression algorithms, and new ways of storing and accessing
data for analysis and to adapt workflows to run on future computing
infrastructures.

@@

Reproducibility of scientific results goes in hand with the need to preserve both the data and the software.
Section~\ref{data-and-software-preservation} develops this latter topic where the FAIR principles of data management are embraced.
